\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{xcolor}
\definecolor{oldred}{rgb}{0.6,0,0}
\definecolor{newgreen}{rgb}{0,0.45,0}
\newenvironment{old}{\par\noindent\textcolor{oldred}{\textbf{OLD:}}\small\color{oldred}\verbatim}{\endverbatim\normalsize\color{black}}
\newenvironment{new}{\par\noindent\textcolor{newgreen}{\textbf{NEW:}}\small\color{newgreen}\verbatim}{\endverbatim\normalsize\color{black}}

\title{Suggested changes: \texttt{typeD\_decoupling-draft-rev2.tex}\\
$\to$ \texttt{typeD\_decoupling-arxiv-suggested.tex}}
\author{}
\date{3 July 2026}

\begin{document}
\maketitle

\noindent Each item shows the exact source text replaced. Everything not listed is
byte-identical to rev2.

\section*{Abstract}

\subsection*{1. Macro for $\mathfrak{so}$ (consistency with body)}
\begin{old}
was constructed using the representation theory of $U_q(so_{2n})$.
\end{old}
\begin{new}
was constructed using the representation theory of $U_q(\so_{2n})$.
\end{new}
Note: I did \emph{not} touch the index. The abstract's $2n$ vs.\ the body's
$2n+2$ (\S1.1: ``$n=2,3$ in $\mathfrak{so}_{2n+2}$'') use different $n$'s ---
your call whether to reconcile.

\subsection*{2. Broken sentence}
\begin{old}
In the fixed--$q$ regime an exact current--decoupling identity, we prove
\end{old}
\begin{new}
In the fixed--$q$ regime, using an exact current--decoupling identity, we prove
\end{new}

\section*{Section 1: Introduction}

\subsection*{3. Subject--verb agreement and typo}
\begin{old}
models have received attention in the mathematical and physics liteature.
\end{old}
\begin{new}
models has received attention in the mathematical and physics literature.
\end{new}

\subsection*{4. Missing hyphen}
\begin{old}
Kardar--Parisi Zhang (KPZ)
\end{old}
\begin{new}
Kardar--Parisi--Zhang (KPZ)
\end{new}

\subsection*{5. Wrong part of speech}
\begin{old}
two species of particles hop asymmetry on a one--dimensional lattice
\end{old}
\begin{new}
two species of particles hop asymmetrically on a one--dimensional lattice
\end{new}

\subsection*{6. Stray space before comma}
\begin{old}
when $q\rightarrow 1$ , one is
\end{old}
\begin{new}
when $q\rightarrow 1$, one is
\end{new}

\subsection*{7. \S1.3: \texttt{prop:sym} labels a Corollary, not a Proposition}
\begin{old}
the species current at all (Proposition~\ref{prop:sym}).
\end{old}
\begin{new}
the species current at all (Corollary~\ref{prop:sym}).
\end{new}

\section*{Section 1.6: Acknowledgements}

\subsection*{8. Typo}
\begin{old}
Digital nnovation
\end{old}
\begin{new}
Digital Innovation
\end{new}

\subsection*{9--11. Straight quotes to LaTeX quotes (3 places)}
\begin{old}
occurred at "Recent Developments in Stochastic Duality" in Eindhoven
NWO grant 613.001.753 "Duality for interacting particle systems."
at the workshop "Universality in the Kardar-Parisi-Zhang class and random
matrix theory."
\end{old}
\begin{new}
occurred at ``Recent Developments in Stochastic Duality'' in Eindhoven
NWO grant 613.001.753 ``Duality for interacting particle systems.''
at the workshop ``Universality in the Kardar-Parisi-Zhang class and random
matrix theory.''
\end{new}

\section*{Section 2}

\subsection*{12. Forward reference to Proposition \texttt{prop:orth} (stated later)}
\begin{old}
sector--reweighted $\varpi\ne\nu$ of Proposition~\ref{prop:orth}. The proof
\end{old}
\begin{new}
sector--reweighted $\varpi\ne\nu$ of Proposition~\ref{prop:orth} below. The proof
\end{new}

\subsection*{13. Remark \texttt{rem:orthstatus}: draft language}
\begin{old}
is deferred to the final version. In regime (B)
\end{old}
\begin{new}
is deferred to future work. In regime (B)
\end{new}

\section*{Section 4}

\subsection*{14. Lemma \texttt{lem:free}: forward references to later lemmas}
\begin{old}
walk on $\Z\setminus\{0\}$ of Lemmas~\ref{lem:Rlclt} and \ref{lem:occ} is
reversible
\end{old}
\begin{new}
walk on $\Z\setminus\{0\}$ of Lemma~\ref{lem:Rlclt} below and of
Lemma~\ref{lem:occ} in \S\ref{sec:cross} is reversible
\end{new}

\section*{Section 5}

\subsection*{15. Remark \texttt{rem:boundstate}: Corollary, not Proposition}
\begin{old}
By Proposition~\ref{prop:sym} below it enters the species fields
\end{old}
\begin{new}
By Corollary~\ref{prop:sym} below it enters the species fields
\end{new}

\section*{Section 6}

\subsection*{16. Aldous's criterion is a Proposition, not a Theorem}
\begin{old}
Theorems~\ref{thm:mitoma}--\ref{prop:aldous}) and uniqueness of the linear
\end{old}
\begin{new}
Theorem~\ref{thm:mitoma} and Proposition~\ref{prop:aldous}) and uniqueness of
the linear
\end{new}

\subsection*{17. Lemma \texttt{lem:sector} proof: $h_i$ was never defined}
\begin{old}
The two measures differ by the factor $h_1(N_1)h_2(N_2)$ of \eqref{eq:omegadef}
(times constants), so the conditionals agree,
\end{old}
\begin{new}
The two measures differ by the factor $h_1(N_1)h_2(N_2)$ (times constants), where
$h_i(N):=q^{N(N-1)}\big(\alpha_i q^{2N-2|\Lambda|};q^2\big)_\infty$ is the sector
reweighting of \eqref{eq:omegadef}, so the conditionals agree,
\end{new}

\section*{Section 7}

\subsection*{18. Moved Lemma \texttt{lem:price} (Price/Sheppard)}
The lemma was stated just before Theorem \texttt{thm:closed}, but it is used
only in the proof of Proposition \texttt{prop:struve}, which comes
$\sim$180 lines \emph{earlier}. The lemma block is moved (text unchanged) to
just before Proposition \texttt{prop:struve}, with the lead-in sentence changed:
\begin{old}
The positive parts of the limiting mixture carry a second closed form.
\end{old}
\begin{new}
The positive parts of the limiting mixture carry a second closed form. Its proof
uses two classical facts about the standard bivariate normal.
\end{new}
and the sentence ``We use two classical facts about the standard bivariate
normal.'' deleted from the old location.

\subsection*{19. Lemma \texttt{lem:crossbridge} proof: internal script path}
\begin{old}
precision for $L\le6$ (\texttt{revision\_checks/check\_crossbridge.py}).
\end{old}
\begin{new}
precision for $L\le6$ (script included among the ancillary files).
\end{new}

\section*{Section 8}

\subsection*{20. Draft-revision language before Proposition \texttt{prop:occ}}
\begin{old}
$a_{\pm1}-c_{\pm1}=-4q^2$. Two corrections to an earlier version of this draft are
required here, and we record them precisely.
\end{old}
\begin{new}
$a_{\pm1}-c_{\pm1}=-4q^2$. Two points require care here --- the sticky bound state is
overweighted in the occupation measure, and the combination supplies the $\sqrt s$
scaling but not the measured constant (\S\ref{sec:numerics}) --- and we record the
occupation asymptotics precisely.
\end{new}
Please check this rephrasing says what you mean.

\section*{Section 9: Status paragraph}

\subsection*{21. Ancillary files}
\begin{old}
are reproduced by scripts to be included as ancillary files.
\end{old}
\begin{new}
are reproduced by scripts included as ancillary files with the arXiv submission.
\end{new}
This (and item 19) commit you to actually attaching the
\texttt{revision\_checks} scripts at submission --- revert both if you won't.

\section*{Noticed but left unchanged}
\begin{itemize}
\item The AI-authorship paragraph appears in both the abstract and \S1.5;
arXiv indexes abstracts. Kept as is.
\item Lemma \texttt{lem:eps} is a proof sketch and Remark \texttt{rem:orthstatus}
defers the infinite-volume step; the Status paragraph discloses both. Kept as is.
\end{itemize}

\end{document}
